Assesing Health Care Coverage and Access Utilizing the National Health Interview Survey

### 2017-03-08 paper/paper.Rmd

# CONLUSION
Final summary and a description of how your system could be extended.

>>>>

# CONLUSION
Our motivation to focus on healthcare was influenced from our class discussions, guest speakers, and even or own personal experiences as healthcare beneficiaries. We observe how the life of other individuals are impacted by the opportunities to attain healthcare coverage. Through our research project studied how health expenditure changed from 2005-2015 for individuals. Our findings help support that idea individuals are mostly spending about less than five-hundred dollars per year on medical charges. This information could be helpful to help develop better health care options to target this population, as they seem to represent a bigger portion of those who spend between five-hundred to roughly five-thousand dollars per year.

Another finding of our research consisted of how of an impact did education attainment have on healthcare access. One point of interest in the educational system was high school. High school was a point that indicated a change in healthcare accessibility. Those who went to pursue higher education were observed to attain their coverage through their workforce. This is something that differs from the idea that higher education leads to more money which ultimately implies that you access for healthcare coverage from your own earnings. It is interesting to realize that the workforce could influence a person access to healthcare.

Our last section of research consisted of the overall population and how the proportions of healthcare coverage can differ. We realize that the proportion of those who have some sort of healthcare coverage is larger than the proportion of those who lack coverage. This, in our perspective, is a positive finding as it is an indicator that more people have access to healthcare.
A final suggestion of our study is that we hope to gain more information on the process of government’s funding. To be more specific we want to gain information on the exact journey that government funds travel. We wish to know how certain policies contribute to the healthcare funding of diverse organizations. Our hopes to to find where government funding is increasing the accessibility of healthcare coverage for any individual that wished to attain it.
